---
title: "Neurovault API"
author: "John Muschelli"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Neurovault API}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


The NeuroVault database (https://neurovault.org/) is a:

> place where researchers can publicly store and share unthresholded statistical maps, parcellations, and atlases produced by MRI and PET studies.

This allows researchers to compare results from multiple studies.

The NeuroVault API (https://neurovault.org/api-docs) allows users to access this data with some calls to a RESTful API.

The `neurovault` package wraps these commands using `httr`.   Here we will look

```{r}
library(neurovault)
res = nv_collection_images(id = 77)
df = results_to_df(res$content$results)
head(df)
```


## Atlases

We can download and view a labeled atlas for the results:

```{r}
library(neurobase)
res = download_nv_atlas(id = 1408)
atlas = readnii(res$outfile[1])
ortho2(atlas)
```


## NIDM Results

You can access the neuroimaging data model (NIDM) (http://nidm.nidash.org/) information using:

```{r}
nidm = nv_nidm_results()
```

